A holographic approach to the six-dimensional superconformal index

### 2022-10-13 fivebranes/index.tex
index

Moreover, the deformation retraction along the fibers $(R\times \C^{2})_{(t,p)}- 0 \to S^{4}_{(t,p)}$ induces a quasi-isomorphism
\[
\left (\Gamma \left (S^{4}_{(t,p)}, \cA^{\bullet}_{\mathring M/\R_{>0}\times Z}(L) \right ) ; \thfd_{0}\right) \cong \left ( \Gamma \left ( \cA^{\bullet}_{(\R\times \C^{2})_{(t,p)} - 0}(L|_{{(\R\times \C^{2})_{(t,p)} - 0}) \right ); \thfd \right )
\]

@@

\begin{lem}
  The cohomology of

  \[\left ( \Gamma \left ( \cA^{\bullet}_{(\R\times \C^{2})_{(t,p)} - 0}(L|_{{(\R\times \C^{2})_{(t,p)} - 0}) \right ); \thfd \right ) \]

    is the complex given by
     \beqn
  %\begin{tikzcd}
  %  + & - \\ \hline
%H^\bu \left ( \Gamma ( \cA^{\bu}_{(\R\times\C^2)-0}), \thfd \right )\{\partial_{w_a}, \partial_{z_i}\}  \ar[r, dotted, "D_{\Omega}"] & %H^\bu \left ( \Gamma ( \cA^{\bu}_{(\R\times\C^2)-0}), \thfd \right )  [z_1,z_2,z_3] \\
%H^\bu \left ( \Gamma ( \cA^{\bu}_{(\R\times\C^2)-0}), \thfd \right )  \ar[r, dotted, "D"] & H^\bu \left ( \Gamma ( \cA^{\bu}_{(\R\times\C^2)-0}), \thfd \right )  [z_1,z_2,z_3]\{dw_a, dz_i\}

 %\end{tikzcd}
\eeqn
\end{lem}

Now the THF cohomology
\[\left ( \Gamma ( \cA^{\bu}_{(\R\times\C^2)-0}), \thfd \right )\]
has a natural pairing, which combines with the natural pairing between vector fields and one-forms to give the desired pairing.

>>>>

Moreover, the deformation retraction along the fibers $(R\times \C^{2})_{(t,p)}- 0 \to S^{4}_{(t,p)}$ induces a quasi-isomorphism
\[
\left (\Gamma \left (S^{4}_{(t,p)}, \cA^{\bullet}_{\mathring M/\R_{>0}\times Z}(L) \right ) ; \thfd_{0}\right) \cong \left ( \Gamma \left ( \cA^{\bullet}_{(\R\times \C^{2})_{(t,p)} - 0}(L|_{{(\R\times \C^{2})_{(t,p)} - 0}}) \right ); \thfd \right )
\]

@@

\begin{lem}
The cohomology of
\[
\left ( \Gamma \left ( \cA^{\bullet}_{(\R\times \C^{2})_{(t,p)} - 0}(L|_{{(\R\times \C^{2})_{(t,p)} - 0}}) \right ); \thfd \right ) 
\]
is the complex given by
\beqn
\begin{tikzcd}
  + & - \\ \hline
H^\bu \left ( \Gamma ( \cA^{\bu}_{(\R\times\C^2)-0}), \thfd \right )\{\partial_{w_a}, \partial_{z_i}\}  \ar[r, dotted, "D_{\Omega}"] & %H^\bu \left ( \Gamma ( \cA^{\bu}_{(\R\times\C^2)-0}), \thfd \right )  [z_1,z_2,z_3] \\
H^\bu \left ( \Gamma ( \cA^{\bu}_{(\R\times\C^2)-0}), \thfd \right )  \ar[r, dotted, "D"] & H^\bu \left ( \Gamma ( \cA^{\bu}_{(\R\times\C^2)-0}), \thfd \right )  [z_1,z_2,z_3]\{dw_a, dz_i\}
\end{tikzcd}
\eeqn
\end{lem}

Now the THF cohomology
\[
\left ( \Gamma ( \cA^{\bu}_{(\R\times\C^2)-0}), \thfd \right )
\]
has a natural pairing, which combines with the natural pairing between vector fields and one-forms to give the desired pairing.
